\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}

\title{Development Plan\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 24, 2024 & Tarnveer Takhtar, Matthew Bradbury & Initial Draft\\
\bottomrule
\end{tabularx}
\end{table}

\newpage{}

This report outlines the key aspects of our project, including our structured 
team meeting and communication plans. It details the roles and responsibilities of team members, 
our workflow plan, and our project decomposition and scheduling strategy. Additionally, it covers our proof of concept demonstration plan, the expected 
technology stack, and the coding standards we will adhere to. The appendices include reflections and our
team charter, which highlights our external goals, attendance expectations, and accountability measures.

\section{Confidential Information?}

No confidential information present at this time.

\section{IP to Protect}

No IP to protect at this time.

\section{Copyright License}
Our project will be using the MIT License.

\section{Team Meeting Plan}

We will be meeting once a week, apart from lecture times, in a physical location on 
McMaster campus. Alternatively, the meeting can be held virtually on Discord or Microsoft Teams incase of
unforeseen circumstances.\\

We will provide our advisor with updates bi-weekly, scheduling an meeting
for larger updates and sending an email for smaller updates. Meetings will
be held virtually unless for specific reasons. Virtual meetings will be hosted on
Microsoft Teams.\\

For each meeting the scheduler of the meeting will be the chair. 
For recurring weekly meetings, the team lead will be the chair. 
Agenda will be prepared by the chair of the meeting.

\section{Team Communication Plan}

Github issues, and a regularly updated Kanban board using those issues, will be used as a means of asynchronous communication 
between members and our Advisor outside of regularly scheduled meetings hosted on Microsoft Teams. 
Discord will be used for general communications between team members. Our Advisor will be contacted via Email or Microsoft Teams.

\section{Team Member Roles}
\noindent Team Lead:\\
Tarnveer Takhtar\\
\\
Approver:\\
Matthew Bradbury\\
\\
Reviewer(s):\\
Harman Bassi\\
Kyen So\\
\\
Administrator:\\
Kyen So\\
\\
Coordinator:\\
Harman Bassi\\

\section{Workflow Plan}

We will be using a branch for each Revision, and separate branches for each
major code features. Pull requests will be reserved for merging feature branches,
while documentation changes will be manually reviewed and edited.\\

Github issues will be created for any tasks as per the course outline, issues will also be created for code features.
Issue priority and classification will be designated by both deadline, and if it is a pre-requisite of other tasks.
Issues will be assigned accordingly as discussed within our meetings. 
If any discrepancies are found within the documentation, an issue will be made, and assigned.\\

GitHub Actions will be used to handle CI/CD, triggered each time a pull request occurs for the codebase of the project. 
A predefined linter will go over the code ensuring consistency with the chosen linter's standard. 
Additional workflow tests may also be present to ensure compatibility.


\section{Project Decomposition and Scheduling}

Our Github project will consist of a Kanban board, highlighting the tasks that still need to be done, in progress or completed.\\
\\
\noindent Link to Kanban Board:
\noindent\href{https://github.com/users/takhtart/projects/3}{https://github.com/users/takhtart/projects/3}\\
\\
The Kanban board will contain a high-level overview of the tasks that need to be done, 
with priority based on deadlines provided by the course outline.

\section{Proof of Concept Demonstration Plan}

\subsection*{Significant Risks}
\begin{enumerate}
\item Project Complexity: The primary risk is the potential complexity of the project, which may be greater than initially anticipated. 
Our team welcomes the challenges associated with this project however, we must understand the risks of taking on a project where we have no experience in the specific domain.

\item Kinect Sensor Performance: Another critical concern is the performance of the provided Kinect sensor, both during the development phase and the demonstration. 
Ensuring the sensor functions optimally and produces a quality real-time point cloud image is crucial for the project's success.

\end{enumerate}

Overall, The performance and reliability of the Kinect sensor and the implementation complexity of the detecting people when only partially visible are our main concerns regarding this project.

\subsection*{Demonstration Plan}

To demonstrate that these risks can be overcome, we plan on showcasing the system's ability to reliably identify people \textbf{not} obscured by any objects (base case). 
This will be a key achievement for our team, instilling confidence within our team that we can take on the primary challenge of identifying people when obscured.
This process will also present the Kinect sensor's performance during both development and the demo, providing more first hand knowledge on the sensor's benefits and drawbacks we should be aware of.

\section{Expected Technology}

We plan to use Python as our primary programming language. 
Python is well-suited for data processing and machine learning, which we will likely need for our project.
We anticipate utilizing libraries such as Open3D for handling point cloud data with a Kinect as our input. 
We may also use NumPy and SciPy for numerical computations, and Scikit-learn for machine learning tasks.\\

Additionally, we may require the use of deep learning frameworks like TensorFlow or PyTorch to train our own models given that it's unlikely there are any existing models for the problem we're trying to solve.
To maintain code quality, we will employ tools like Flake8 for linting and Pytest for unit testing. 
For code coverage we plan use Coverage.py to ensure thorough testing.
For CI, we will likely use GitHub Actions to automate testing and deployment.
Collaboration and version control will be conducted through Git and GitHub. Github Projects will be used to manage opened issue tickets, and be our primary tracker for project progression.
Performance monitoring tools such as Valgrind may be considered for optimizing critical code sections (optimizing real-time detection). 

\section{Coding Standard}
The coding standard we will adopt will be Pep 8. 

\newpage{}

\section*{Appendix --- Reflection}

\input{../Reflection.tex}

\newpage{}

\section*{Appendix --- Team Charter}

\subsection*{External Goals}

The team's external goals for this project are to create an impressive project
to discuss during interviews. Additionally, we aim to showcase a challenging
and noteworthy project at the capstone convention. We also want to develop new skills 
and refine our existing ones throughout this project.

\subsection*{Attendance}

\subsubsection*{Expectations}

The expectation is that members clearly communicate their availability,
and give at least 24 hour notice when not being able to attend meetings.
If a member needs to skip/leave early, they are expected to communicate 
what work they will complete prior to the next meeting and ensure that
they are up to date on any project changes. While there is no \% of
meetings that must be attended, we will be using group consensus to
determine if one particular group member is missing a worrying number
of meetings.

\subsubsection*{Acceptable Excuse}

An acceptable excuse for missing a meeting or deadline would be any truly
unforeseen/unavoidable engagement which requires immediate attention or any engagement 
that is properly communicated beforehand. The second type of excuse will not be 
permitted if the rest of the group feels that an individual member has missed too 
many meetings/deadlines.

\subsubsection*{In Case of Emergency}

In case of emergency, the individual should convey exactly what they can and cannot accomplish to
the team, and ensure that they complete an adequate amount of work at a later date 
for whoever ends up covering.

\subsection*{Accountability and Teamwork}

\subsubsection*{Quality}

Team members are expected to adequately prepare for team meetings. This means completing 
agreed upon work prior to meeting times, barring a reasonable excuse. For supervisor/TA
meetings, members are expected to adequately understand the reason for the meeting enough
to contribute unique ideas/questions to the conversation.\\ 

Regarding quality of work, members are expected to complete work at a reasonable pace, allowing room 
for adequate review to take place prior to deadlines. The work should also be done at a quality
similar to the others, i.e. everyone is contributing at a quality similar to the person of highest
engagement/quality level.

\subsubsection*{Attitude}

The team's expectations are that each member completes work with a level of engagement
relatively similar to other team members. When providing ideas/interactions, it is 
expected that each member is treated with respect.

\subsubsection*{Stay on Track}

We will use Github projects to ensure that we are on track. Each task to work on
will be stored in an issue, which will have up to date deadlines attached to them, 
as well as the assignee(s). This will give us the ability to check up and see if 
tasks are being worked on/reviewed at a timely pace. On top of issues, we will 
be looking at commits and team meeting attendance to gauge contributions.\\

In the event that members aren't contributing their fair share, that member will have
to purchase snacks for the next team meeting. We will also have a group meeting with 
them to discuss steps to improve and expectations. If the behaviour continues further, 
we will escalate the issue to a TA/professor.

\subsubsection*{Team Building}

Team cohesion will be built through friendly conversation/banter and engaging
in fun/relaxing group activities.

\subsubsection*{Decision Making} 

We will make decisions based on group consensus, and if the vote isn't unanimous we will try to solve the dispute
via discussion until the decision is unanimous. If disagrees propagate further, we will escalate to asking our supervisor
or TA for advice on how to proceed.

\end{document}