\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation.

\section{Team Meeting Attendance}

\begin{table}[H]
    \centering
    \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Meetings}\\
    \midrule
    Total & 9\\
    Tarnveer Takhtar & 9\\
    Matthew Bradbury & 9\\
    Harman Bassi & 9\\
    Kyen So & 9\\
    \bottomrule
    \end{tabular}
    \end{table}

Two meeting were for divvying up the VnV Plan/Report documentation and the remaining meetings were to work on the application and doing the revison 1 changes. 
These meetings also include the work sessions for the Research Manual. 
The code meetings were mainly work sessions to test out and optimize code for a better algorithm and also the completion of the new requirement.

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
    \centering
    \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Meetings}\\
    \midrule
    Total & 7\\
    Tarnveer Takhtar & 7\\
    Matthew Bradbury & 7\\
    Harman Bassi & 7\\
    Kyen So & 7\\
    \bottomrule
    \end{tabular}
    \end{table}

There was one in person meeting with Dr.Bone. 
This was to show the current progress of the team after the Rev 0 demo and to discuss 
further methods to improve the current implementation and to talk about the new requirement.
The remaining of the meetings were all held on Teams and ranged from quick posts about the teams 
progress and videos showcasing the code so far.
    

\section{Lecture Attendance}

\begin{table}[H]
    \centering
    \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Lectures}\\
    \midrule
    Total & 1\\
    Tarnveer Takhtar & 1\\
    Matthew Bradbury & 1\\
    Harman Bassi & 1\\
    Kyen So & 1\\
    \bottomrule
    \end{tabular}
    \end{table}


\section{TA Document Discussion Attendance}

\begin{table}[H]
    \centering
    \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Lectures}\\
    \midrule
    Total & 1\\
    Tarnveer Takhtar & 0\\
    Matthew Bradbury & 0\\
    Harman Bassi & 0\\
    Kyen So & 0\\
    \bottomrule
    \end{tabular}
    \end{table}

We had forgot about the meeting as we were swamped with work from other classes. 
We reached out to Hunter after missing the meeting to explain what happened. 

\section{Commits}


\begin{table}[H]
    \centering
    \begin{tabular}{lll}
    \toprule
    \textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
    \midrule
    Total & 136 & 100\% \\
    Tarnveer Takhtar & 43 & 31.6\%\\
    Matthew Bradbury & 38 & 27.9\%\\
    Harman Bassi & 39 & 28.7\%\\
    Kyen So & 16 & 11.8\%\\
    \bottomrule
    \end{tabular}
    \end{table}

Commit numbers are based on the Insights/Contributors tab, contribution numbers do not include any co-authored commits (avoid double counting).
The number of commits for Tarnveer and Kyen have not seen much change because they have mainly been focused on completing the code aspect of the project 
and so they have not merged with main. While Matthew and Harman worked on revision 1 changes.

\section{Issue Tracker}

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Tarnveer Takhtar & 2 & 11\\
Matthew Bradbury & 23 & 33\\
Harman Bassi & 46 & 28\\
Kyen So & 0 & 9\\
\bottomrule
\end{tabular}
\end{table}

\end{document}