\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

Information on the demonstration plan can be found in the \textit{Proof of Concept Demonstration Plan} section of the \href{https://github.com/takhtart/PCD/blob/main/docs/DevelopmentPlan/DevelopmentPlan.pdf}{Development Plan}.

\section{Team Meeting Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 8\\
Tarnveer Takhtar & 8\\
Matthew Bradbury & 8\\
Harman Bassi & 8\\
Kyen So & 8\\
\bottomrule
\end{tabular}
\end{table}


Two meetings per submission (one for dividing work amongst members and one for review/editing). 
Dividing the work was done in-person, while meeting for editing/review was typically online. All members have a similar schedule, 
and so most discussions occured in person organically without the need of scheduling a formal meeting. 

\section{Supervisor/Stakeholder Meeting Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2\\
Tarnveer Takhtar & 2\\
Matthew Bradbury & 2\\
Harman Bassi & 2\\
Kyen So & 2\\
\bottomrule
\end{tabular}
\end{table}

We have had two meetings with our supervisor/stakeholder Dr. Gary Bone. During the first meeting, we discussed the scope of the project and informed Dr. Bone of our interest in the project. 
We scheduled a second meeting at a later date to discuss various questions we had for Dr. Bone.

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 10\\
Tarnveer Takhtar & 10\\
Matthew Bradbury & 10\\
Harman Bassi & 10\\
Kyen So & 10\\
\bottomrule
\end{tabular}
\end{table}


\section{TA Document Discussion Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Discussions}\\
\midrule
Total & 3\\
Tarnveer Takhtar & 2\\
Matthew Bradbury & 3\\
Harman Bassi & 3\\
Kyen So & 3\\
\bottomrule
\end{tabular}
\end{table}

Tarnveer was unable to attend one of the informal TA Document Discussion meetings due to an illness which he informed the team ahead of time. 
He reached out to learn about what was discussed afterwards.

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 56 & 100\% \\
Tarnveer Takhtar & 25 & 45\%\\
Matthew Bradbury & 13 & 23\%\\
Harman Bassi & 8 & 14\%\\
Kyen So & 10 & 18\%\\
\bottomrule
\end{tabular}
\end{table}

Commit numbers are based on the Insights/Contributors tab, contribution numbers do not include any co-authored commits (avoid double counting).

\section{Issue Tracker}



\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Tarnveer Takhtar & 0 & 6\\
Matthew Bradbury & 8 & 8\\
Harman Bassi & 0 & 4\\
Kyen So & 0 & 4\\
\bottomrule
\end{tabular}
\end{table}

\section{CICD}

We will be implementing CI/CD using a combinitaion of Github Actions and Clang-Tidy linter throughout the development process of our software system. 
The action will be used for staic code analysis, ensuring our code meets proper coding standards. 
The action will trigger against every commit and pull request, ensuring the code quality remains consistent throughout the developement process.

\end{document}