\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the POC demo and the Rev
0 demo.

\section{Demo Plans}

The plan is to showcase changes made from POC. The main target is to highlight the HSV Mask to better detect humans based off of skin color. We are also showcasing region growing from those skin points to find the whole human. 
Finally, mention segmentation of different human parts from the processed cluster identified as a human.  
More information on the demonstration plan can be found in the \textit{Proof of Concept Demonstration Plan} section of the \href{https://github.com/takhtart/PCD/blob/main/docs/DevelopmentPlan/DevelopmentPlan.pdf}{Development Plan}.


\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 7\\
Tarnveer Takhtar & 7\\
Matthew Bradbury & 7\\
Harman Bassi & 7\\
Kyen So & 7\\
\bottomrule
\end{tabular}
\end{table}

One meeting was for divvying up the MIS/MG documentation and the remaining meetings were to work on the application itself.
The code meetings were mainly work sessions to test out and optimize code for a better algorithm. 

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 1\\
Tarnveer Takhtar & 1\\
Matthew Bradbury & 1\\
Harman Bassi & 1\\
Kyen So & 1\\
\bottomrule
\end{tabular}
\end{table}

There was one in person meeting with Dr.Bone. 
This was to show the current progress of the team after the POC demo and to discuss 
further methods to improve the current implementation.

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Tarnveer Takhtar & 2\\
Matthew Bradbury & 2\\
Harman Bassi & 2\\
Kyen So & 2\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Tarnveer Takhtar & 1\\
Matthew Bradbury & 1\\
Harman Bassi & 1\\
Kyen So & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 83 & 100\% \\
Tarnveer Takhtar & 38 & 45.8\%\\
Matthew Bradbury & 17 & 20.5\%\\
Harman Bassi & 13 & 15.7\%\\
Kyen So & 15 & 18.0\%\\
\bottomrule
\end{tabular}
\end{table}

Commit numbers are based on the Insights/Contributors tab, contribution numbers do not include any co-authored commits (avoid double counting).

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Tarnveer Takhtar & 2 & 10\\
Matthew Bradbury & 23 & 12\\
Harman Bassi & 0 & 8\\
Kyen So & 0 & 8\\
\bottomrule
\end{tabular}
\end{table}

\section{CICD}

We will be implementing CI/CD using a combinitaion of Github Actions and Clang-Tidy linter throughout the development process of our software system. 
The action will be used for staic code analysis, ensuring our code meets proper coding standards. 
The action will trigger against every commit and pull request, ensuring the code quality remains consistent throughout the developement process.

\end{document}